A fully labelled proof system for intuitionistic modal logics

### 2020-09-15 FullyLabelled/JLC/system.tex
reformating extensions

>>>>

\todo{}
\sonia{
	The rule corresponding to the $F_1$ was obtained through the standard axioms-to-rule procedure that is well known for geometric axioms. 
%
A similar rule can already be found in~\cite{maffezioli2014}.
%
It corresponds to attributing a positive polarity to both relational and pre-order atoms.

$$\vlinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$

On the other hand, a different rule for $F_1$ could be obtained in the style of Vigano, that is, by polarising both relational and pre-order atoms negatively, as follows:

$$\vliiinf{}{\lb u \mbox{ fresh}}{\B, \Gamma \SEQ \Delta}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \futs yz, \Gamma \SEQ \Delta}{\futs xu, \accs uz, \Gamma \SEQ \Delta}$$

\lutz{we should say that this is pretty pointless wrt proof search.}
It is also possible to design a "mixed" rule, by considering relational atoms positively and pre-order atoms negatively:

$$\vliinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$

Or vice-versa:

$$\vliinf{}{\lb u \mbox{ fresh}}{\B, \futs yz, \Gamma \SEQ \Delta}{\B, \futs yz, \accs xy, \Gamma \SEQ \Delta}{\futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
}
